---
title: "MATSim-freight"
output:
  html_document:
    df_print: paged
  pdf_document: default
---

# Example plots with R

This file is not meant as a ready-to-run plot generator, but as a stepping stone to create own plots using the data by providing code examples.
For quick results, change the paths in the setup chunk to your analysis output files and compile the Document.

```{r setup, message=FALSE, warning=FALSE, echo=FALSE}
library(tidyverse)
library(pracma)
library(sjmisc)

chessvehicleStats <- read_tsv("../Dokumentation/output_chessboard/freightVehicleStats.tsv") %>% mutate(travelDistance=travelDistance/1000)
chesscarrierStats <- read_tsv("../Dokumentation/output_chessboard/carrierStats.tsv")
chesstripStats <- read_tsv("../Dokumentation/output_chessboard/freightVehicleTripStats.tsv")
chessserviceStats <- read_tsv("../Dokumentation/output_chessboard/serviceStats.tsv")
chessshipmentStats <- read_tsv("../Dokumentation/output_chessboard/shipmentStats.tsv")

KMTvehicleStats <- read_tsv("../Dokumentation/output_KMT/freightVehicleStats.tsv") %>% mutate(travelDistance=travelDistance/1000)
KMTcarrierStats <- read_tsv("../Dokumentation/output_KMT/carrierStats.tsv")
KMTtripStats <- read_tsv("../Dokumentation/output_KMT/freightVehicleTripStats.tsv")
KMTserviceStats <- read_tsv("../Dokumentation/output_KMT/serviceStats.tsv")
KMTshipmentStats <- read_tsv("../Dokumentation/output_KMT/shipmentStats.tsv")
```

## Comparison of "VehicleTypes
### Travel Distance of "heavy" vehicles

```{r}
KMTvehicleStats %>% filter(grepl("heavy", VehicleType)) %>% 
                             ggplot()+
                            geom_density(mapping=aes(x=travelDistance, group=VehicleType, fill=VehicleType), alpha=0.5)
```
### Are there significantly different loading/unloading times for vehicles?

```{r fig.cap ="travelDistance distribution of vehicle types", echo=FALSE, warning=FALSE}
ggplot(KMTvehicleStats)+
  geom_point(mapping=aes(x=usageTime, y=roadTime))
```

### Do retail chains have similar delivery strategies?

```{r fig.cap ="travelDistance distribution of vehicle types", echo=FALSE, warning=FALSE}
### leg Count density of "TROCKEN" carriers
KMTvehicleStats %>% filter(grepl("TROCKEN", CarrierId)) %>% ggplot()+
  facet_wrap(vars(CarrierId))+
  geom_density(mapping=aes(x=legCount))
```

## Shipment export
### Economy of Scale: Cost per shipment for carriers

```{r}
time_chessserviceStats <- chessserviceStats %>% mutate(ArrivalTime=as.numeric(substr(ArrivalTime, 2, length(ArrivalTime))))

carriercost <- KMTcarrierStats  %>% group_by(carrierId) %>% summarise(Cost=sum(totalCost)) %>% select(carrierId, Cost)

shipmentcount <- KMTshipmentStats %>% group_by(carrierId) %>% summarise(count=n()) 
  
out <- carriercost  %>% inner_join(shipmentcount, by = "carrierId") %>% mutate(costPerShipment=count/-Cost)

ggplot(out)+
  geom_point(mapping=aes(x=count, y=costPerShipment))+
  labs(x="Shipment Count of Carrier", y="Cost per Shipment")
```

### Distance shipments are travelling (~ hub density)

```{r}
KMTshipmentStats %>% filter(grepl("TROCKEN", carrierId)) %>% 
  ggplot() + 
  facet_wrap(vars(carrierId))+
  geom_density(mapping=aes(x=beelineDistance))
```

### Services from the chessboard-example

```{r}
# how good are guesses?
ggplot(time_chessserviceStats)+
  geom_point(mapping=aes(x=ArrivalTime, y=TourETA))

# tagesganglinie
ggplot(time_chessserviceStats)+
  geom_density(mapping=aes(x=TourETA))+labs(x="Estimated Arrival Time")
```
 
 
 
 